Neural fields with different embedding dimensionality can express identical dynamics

### 2024-02-20 paper/manuscript.tex
PLOS compliant text

%% NETN Template file

%% Documentclass:
\documentclass[NETN,manuscript]{stjour-new}

%% Or,
%% For production only, need .otf fonts, private MIT logo files,
%% and need to use lualatex:
% \documentclass[finalfonts,NETN]{stjour-new}

%%%%%%%%%%% Article Set-Up %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Article Type:

%% Choose one of these options, (Default is Research).
%% Research
%% Methods 
%% Data
%% Review
%% Perspectives

\articletype{Research}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% author definitions should be placed here:

@@

\begin{document}

% TODO: what title is better ?
% \title{Equivalence of neural field dynamics with different embedding dimensionality}
\title{Neural fields with different embedding dimensionality can express identical dynamics}
% \title{Neural dynamics can be equivalently embedded in neural fields of different dimensions}

% \subtitle{<Subtitle Here>} %% Optional subtitle

%% If shortened title for running head is needed so that the article title can fit
%%   in the running head, use [] argument, ie,
%%
%%   \title[Shortened Title for Running Head]{Title of Article}
%%   \subtitle{Subtitle Here}

%%% Author/Affil
%% Since we use \affil{} in the argument of the \author command, we
%% need to supply another version of the author names, without \affil{}
%% to be used for running heads:

\author{Nicole Vadot\affil{1}, Valentin Schmutz\affil{1}, \and Wulfram Gerstner \affil{1}}

\affiliation{1}{LCN, EPFL, Lausanne, Switzerland}

%ie.
%\affiliation{1}{Gatsby Computational Neuroscience Unit, University
%College London, London, United Kingdom}

% \affiliation{2}{Another Department, Institution, City, Country}

%ie
%\affiliation{2}{Center for Studies in
%Behavioral Neurobiology, Concordia University, Montreal, Quebec,
%Canada}

\correspondingauthor{Nicole Vadot}{nicole.vadot@epfl.ch}
\correspondingauthor{Valentin Schmutz}{valentin.schmutz@epfl.ch}
\correspondingauthor{Wulfram Gerstner}{wulfram.gerstner@epfl.ch}

% ie,
%\correspondingauthor{Ritwik K. Niyogi}{ritwik.niyogi@gatsby.ucl.ac.uk}

\keywords{Neural fields, Embedding, Dimensionality}

%ie
%\keywords{Work, Leisure, Normative, Microscopic,  Reinforcement Learning, Economics}

\begin{abstract}
Classical neural field models describe interactions between neurons positioned in an embedding; often a physical space (for instance, that of the cortical sheet) or, later, abstract spaces (for instance, that of neuron celltypes), in which the dynamics are highly regular in space and time. Recent improvements in recordings of neural activity have further demonstrated the smoothness of the neural dynamics, when placed in an appropriate embedding space.

@@

We show that embedding spaces are not unique, and more suprisingly, that we can find multiple embedding spaces in different dimensions, which all model identical neural dynamics.
The core of this work lies in the study of bijective mappings $S$ between $[0,1]^2$ and $[0,1]$, which allows mapping a two-dimensional neural field to an equivalent one-dimensional neural field.
This procedure is easily generalized to map between embeddings in arbitrary number of dimensions.
We introduce a measure of locality, which quantifies how the regularity of the neural fields in conserved through the mappings $S$. This allows us to show that the resulting neural field is well-behaved, and can therefore be approximated using classical grid-based methods.
To illustrate these results through numerical models, we describe a coarse-graining procedure enforcing the locality of the numerically applied mappings.
\end{abstract}

% \begin{authorsummary}
% Author Summary here.
% \end{authorsummary}

@@

Early recordings of cats' somatosensory \citep{Mou57} and visual \citep{HubWie62} cortices suggested that the cortical sheet is organized in vertical columns of functionally similar neurons.

The columnar organization of the cortex motivated the design of spatially structured models of neural population dynamics, namely neural field models \citep{WilCow73,Nun74,Ama77}, where the spatial dimensions corresponded to the two dimensions of the cortical sheet.

As models of spatiotemporal neural population dynamics on the cortical sheet, neural field models can be used to explain experimentally observed patterns of cortical activity, such as travelling waves in visual \citep{SatNau12,MulRey14}, somatosensory \citep{PetHah03,FerBol06}, motor \citep{RubRob06,TakKim15}, and hippocampal \citep{LubSia09,PatFuj12,PatSch13} cortices (see \citep{MulCha18} for a review), and are used to model large-scale brain signals, such as electroencephalography (EEG) recordings \citep{Bre17} (see also \citep{DipRan18} for an example of neural field modelling of calcium imaging recording of the visual cortex).

More recent recording methods, especially in rodents, have provided evidence of low-dimensional organization of neuronal activity that does not depend on the physical locations of neurons on the cortical sheet. For example, contrary to cats' visual cortex, the orientation selectivity of pyramidal neurons in a rat's visual cortex does not depend on their locations, that is, orientation selectivity is heterogeneous at any given location \citep{OhkChu05}. Moreover, the activity of interneurons in any small volume of the visual cortex is also heterogeneous and seems to be structured by a low-dimensional manifold of fine cell subtypes \citep{BugDuf22}. The local functional heterogeneity of neuronal activity in the cortex challenges the old concept of functionally homogeneous cortical columns and, with it, classical neural field models.

While, historically, the spatial dimensions in neural field models have been the two dimensions of the cortical sheet (with the notable exception of the ring models for orientation selectivity in the visual cortex \citep{BenBar95} and the head-direction system \citep{Zha96}), the "space" in neural field models does not need to represent physical space but can represent any suitable abstract embedding space. Neural field models with abstract embedding spaces could constitute a generalization of classical neural field theory for cortical networks that are not solely structured by distances of neurons on the cortical sheet.

Moreover, this work is motivated by recent mathematical developments \citep{JabPoy21} in mean-field theories involving the theory of graphons. Informally, these results suggest that, as long as the connectivity scales as $1/N$ (where $N$ is the number of neurons), the dynamics of large networks can be described in the $N \to \infty$ limit by a neural field equation where the embedding is simply the interval $[0,1]$. The main contribution of this paper is the derivation of a method, allowing to explicitly write such a one-dimensional neural field, starting from a known higher-dimensional neural field.

@@

We begin our work by considering a neural field associated with a $p$-dimensional embedding $\Rp$. $h(\vec z, t)$ describes the potential of the neural population at position $\vec z=(z_1,\cdots,z_p)$ in the embedding. The connectivity kernel $w(\vec y, \vec z)$ describes the amplitude of the recurrent currents from the population at $\vec z$ to the population at $\vec y$. Importantly, $w(\vec y, \vec z)$ is a ``smooth'' function in both arguments. This is a natural consequence of the derivation of neural field equations (rigorous proofs of convergence of networks to neural fields are still an active area of study, and we may cite \citep{CheDua19,AGATHENERINE202286} for recent developments).
$\rho(\vec z)$ measures the number of neurons per unit volume of the embedding space, effectively weighing the recurrent currents. The monotonic increasing activation function $\phi(h)$ describes the firing rate of a given neuron (population) with potential $h$. The neural field then evolves according to \autoref{eq:nf-in-rp}:

@@

Let us define a sequence of bijective mappings $S^n$, acting on the $n$-bit truncations of $\vec{v_i}$, as well as the sequence $\alpha_i^{(n)} \in [0,1]$ of positions resulting from the image of $\vec{v_i^{(n)}}$. In the following, we again drop the index $i$ for clarity.

\begin{equation} \begin{aligned}
S^n &: (v_1^{(n)}, v_2^{(n)}) = (0.b_1^1 b_1^2 \cdots b_1^n, 0.b_2^1 b_2^2 \cdots b_2^n) \\
&\mapsto \alpha^{(n)} = 0.b^1 b^2 \cdots b^{2n}
\end{aligned} \end{equation}

We note that we write $\alpha^{(n)}$ using $2n$ bits, which is intuitively the lowest number of bits required so that $S^n$ remains a bijection. More than $2n$ bits could be allowed while maintaining bijectivity, but we omit this possibility, since they wouldn't strictly be required. Effectively, $S^n$ maps between $2\times n$ input bits and $2n$ output bits. In this formulation, it becomes clear that in order to be a bijection, every bit of the input must be used once and only once to form the output. Setting aside bit inversions, this means that $S^n$ defines a permutation of the $2n$ input bits. [TODO: are more details necessary ? I think this is clear enough, though in the thesis manuscript I got over this point in more detail]

@@

\acknowledgments

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% End of Article

% \acknowledgments
% \section{Supporting Information} (optional)
% \section{Competing Interests} (optional)
% \bibliography{<name of .bib file>}

% \acknowledgments
% The Funder and award ID information you input at submission will be introduced by the publisher under a Funding Information head during production. 
% Please use this space for any additional acknowledgements and verbiage required by your funders.

% \section{Supporting Information}
% This is an optional section. Please use this space to provide information about any supporting information referred to in your manuscript.

% \section{Competing Interests}
% This is an optional section. If you declared a conflict of interest when you submitted your manuscript, please  use this space to provide details about this conflict.

% \section{Technical Terms}

% All NETN article types require Technical Terms.

% Identify approximately 10 key terms that are mentioned in your article and whose usage and definition may not be familiar across the broad readership of the journal. 
% Provide brief (20-word or less) definitions for each term, avoiding in these definitions the use of jargon, or highly technical or specialized language. 
% When the article is typeset, the Technical Terms will appear in the margins at or near their first mention in the text.

% In your manuscript, bold the first occurrence of each \textbf{Technical Term} and then provide a list of the terms and their definitions at the end of the manuscript after the references.

%%%%%%%%%%%%%%%%%%%%%%%
%% The bibliography

%% The bibliography is made using only the entries that you cite using 
%% \cite{}, or one of the Natbib citation entries, like \citep{}, \citet{} etc.

\bibliography{references}

%ie.,
%\bibliography{bibsamp}

% \section{Technical Terms}

% \textbf{Technical Term} a key term that is mentioned in an NETN article and whose usage and definition may not be familiar across the broad readership of the journal.

% \textbf{Technical Term} a key term that is mentioned in an NETN article and whose usage and definition may not be familiar across the broad readership of the journal.

% \textbf{Technical Term} a key term that is mentioned in an NETN article and whose usage and definition may not be familiar across the broad readership of the journal.

% \textbf{Technical Term} a key term that is mentioned in an NETN article and whose usage and definition may not be familiar across the broad readership of the journal.

>>>>

% Template for PLoS
% Version 3.6 Aug 2022
%
% % % % % % % % % % % % % % % % % % % % % %
%
% -- IMPORTANT NOTE
%
% This template contains comments intended 
% to minimize problems and delays during our production 
% process. Please follow the template instructions
% whenever possible.
%
% % % % % % % % % % % % % % % % % % % % % % % 
%
% Once your paper is accepted for publication, 
% PLEASE REMOVE ALL TRACKED CHANGES in this file 
% and leave only the final text of your manuscript. 
% PLOS recommends the use of latexdiff to track changes during review, as this will help to maintain a clean tex file.
% Visit https://www.ctan.org/pkg/latexdiff?lang=en for info or contact us at latex@plos.org.
%
%
% There are no restrictions on package use within the LaTeX files except that no packages listed in the template may be deleted.
%
% Please do not include colors or graphics in the text.
%
% The manuscript LaTeX source should be contained within a single file (do not use \input, \externaldocument, or similar commands).
%
% % % % % % % % % % % % % % % % % % % % % % %
%
% -- FIGURES AND TABLES
%
% Please include tables/figure captions directly after the paragraph where they are first cited in the text.
%
% DO NOT INCLUDE GRAPHICS IN YOUR MANUSCRIPT
% - Figures should be uploaded separately from your manuscript file. 
% - Figures generated using LaTeX should be extracted and removed from the PDF before submission. 
% - Figures containing multiple panels/subfigures must be combined into one image file before submission.
% For figure citations, please use "Fig" instead of "Figure".
% See http://journals.plos.org/plosone/s/figures for PLOS figure guidelines.
%
% Tables should be cell-based and may not contain:
% - spacing/line breaks within cells to alter layout or alignment
% - do not nest tabular environments (no tabular environments within tabular environments)
% - no graphics or colored text (cell background color/shading OK)
% See http://journals.plos.org/plosone/s/tables for table guidelines.
%
% For tables that exceed the width of the text column, use the adjustwidth environment as illustrated in the example table in text below.
%
% % % % % % % % % % % % % % % % % % % % % % % %
%
% -- EQUATIONS, MATH SYMBOLS, SUBSCRIPTS, AND SUPERSCRIPTS
%
% IMPORTANT
% Below are a few tips to help format your equations and other special characters according to our specifications. For more tips to help reduce the possibility of formatting errors during conversion, please see our LaTeX guidelines at http://journals.plos.org/plosone/s/latex
%
% For inline equations, please be sure to include all portions of an equation in the math environment.  For example, x$^2$ is incorrect; this should be formatted as $x^2$ (or $\mathrm{x}^2$ if the romanized font is desired).
%
% Do not include text that is not math in the math environment. For example, CO2 should be written as CO\textsubscript{2} instead of CO$_2$.
%
% Please add line breaks to long display equations when possible in order to fit size of the column. 
%
% For inline equations, please do not include punctuation (commas, etc) within the math environment unless this is part of the equation.
%
% When adding superscript or subscripts outside of brackets/braces, please group using {}.  For example, change "[U(D,E,\gamma)]^2" to "{[U(D,E,\gamma)]}^2". 
%
% Do not use \cal for caligraphic font.  Instead, use \mathcal{}
%
% % % % % % % % % % % % % % % % % % % % % % % % 
%
% Please contact latex@plos.org with any questions.
%
% % % % % % % % % % % % % % % % % % % % % % % %

\documentclass[10pt,letterpaper]{article}
\usepackage[top=0.85in,left=2.75in,footskip=0.75in]{geometry}

% amsmath and amssymb packages, useful for mathematical formulas and symbols
\usepackage{amsmath,amssymb}

% Use adjustwidth environment to exceed column width (see example table in text)
\usepackage{changepage}

% textcomp package and marvosym package for additional characters
\usepackage{textcomp,marvosym}

% cite package, to clean up citations in the main text. Do not remove.
\usepackage{cite}

% Use nameref to cite supporting information files (see Supporting Information section for more info)
\usepackage{nameref,hyperref}

% line numbers
\usepackage[right]{lineno}

% ligatures disabled
\usepackage[nopatch=eqnum]{microtype}
\DisableLigatures[f]{encoding = *, family = * }

% color can be used to apply background shading to table cells only
\usepackage[table]{xcolor}

% array package and thick rules for tables
\usepackage{array}

% create "+" rule type for thick vertical lines
\newcolumntype{+}{!{\vrule width 2pt}}

% create \thickcline for thick horizontal lines of variable length
\newlength\savedwidth
\newcommand\thickcline[1]{%
  \noalign{\global\savedwidth\arrayrulewidth\global\arrayrulewidth 2pt}%
  \cline{#1}%
  \noalign{\vskip\arrayrulewidth}%
  \noalign{\global\arrayrulewidth\savedwidth}%
}

% \thickhline command for thick horizontal lines that span the table
\newcommand\thickhline{\noalign{\global\savedwidth\arrayrulewidth\global\arrayrulewidth 2pt}%
\hline
\noalign{\global\arrayrulewidth\savedwidth}}

% Remove comment for double spacing
%\usepackage{setspace} 
%\doublespacing

% Text layout
\raggedright
\setlength{\parindent}{0.5cm}
\textwidth 5.25in 
\textheight 8.75in

% Bold the 'Figure #' in the caption and separate it from the title/caption with a period
% Captions will be left justified
\usepackage[aboveskip=1pt,labelfont=bf,labelsep=period,justification=raggedright,singlelinecheck=off]{caption}
\renewcommand{\figurename}{Fig}

% Use the PLoS provided BiBTeX style
\bibliographystyle{plos2015}

% Remove brackets from numbering in List of References
\makeatletter
\renewcommand{\@biblabel}[1]{\quad#1.}
\makeatother

% Header and Footer with logo
\usepackage{lastpage,fancyhdr,graphicx}
\usepackage{epstopdf}
%\pagestyle{myheadings}
\pagestyle{fancy}
\fancyhf{}
%\setlength{\headheight}{27.023pt}
%\lhead{\includegraphics[width=2.0in]{PLOS-submission.eps}}
\rfoot{\thepage/\pageref{LastPage}}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrule}{\hrule height 2pt \vspace{2mm}}
\fancyheadoffset[L]{2.25in}
\fancyfootoffset[L]{2.25in}
\lfoot{\today}

%% Include all macros below

\newcommand{\lorem}{{\bf LOREM}}
\newcommand{\ipsum}{{\bf IPSUM}}

%% User macros

@@

%% END MACROS SECTION

\begin{document}
\vspace*{0.2in}

% Title must be 250 characters or less.
\begin{flushleft}
% TODO: what title is better ?
% \title{Equivalence of neural field dynamics with different embedding dimensionality}
% \title{Neural fields with different embedding dimensionality can express identical dynamics}
% \title{Neural dynamics can be equivalently embedded in neural fields of different dimensions}
{\Large
\textbf\newline{Neural fields with different embedding dimensionality can express identical dynamics} % Please use "sentence case" for title and headings (capitalize only the first word in a title (or heading), the first word in a subtitle (or subheading), and any proper nouns).
}
\newline
% Insert author names, affiliations and corresponding author email (do not include titles, positions, or degrees).
\\
Nicole Vadot\textsuperscript{1},
Valentin Schmutz\textsuperscript{1},
Wulfram Gerstner\textsubscript{1}
% Name1 Surname\textsuperscript{1,2\Yinyang},
% Name2 Surname\textsuperscript{2\Yinyang},
% Name3 Surname\textsuperscript{2,3\textcurrency},
% Name4 Surname\textsuperscript{2},
% Name5 Surname\textsuperscript{2\ddag},
% Name6 Surname\textsuperscript{2\ddag},
% Name7 Surname\textsuperscript{1,2,3*},
% with the Lorem Ipsum Consortium\textsuperscript{\textpilcrow}
\\
\bigskip
\textbf{1} LCN, EPFL, Lausanne, Vaud, Switzerland
% \\
% \textbf{2} Affiliation Dept/Program/Center, Institution Name, City, State, Country
% \\
% \textbf{3} Affiliation Dept/Program/Center, Institution Name, City, State, Country
% \\
\bigskip

% Insert additional author notes using the symbols described below. Insert symbol callouts after author names as necessary.
% 
% Remove or comment out the author notes below if they aren't used.
%
% Primary Equal Contribution Note
% \Yinyang These authors contributed equally to this work.

% Additional Equal Contribution Note
% Also use this double-dagger symbol for special authorship notes, such as senior authorship.
% \ddag These authors also contributed equally to this work.

% Current address notes
% \textcurrency Current Address: Dept/Program/Center, Institution Name, City, State, Country % change symbol to "\textcurrency a" if more than one current address note
% \textcurrency b Insert second current address 
% \textcurrency c Insert third current address

% Deceased author note
% \dag Deceased

% Group/Consortium Author Note
% \textpilcrow Membership list can be found in the Acknowledgments section.

% Use the asterisk to denote corresponding authorship and provide email address in note below.
% * correspondingauthor@institute.edu

\end{flushleft}
% Please keep the abstract below 300 words
\section*{Abstract}
Classical neural field models describe interactions between neurons positioned in an embedding; often a physical space (for instance, that of the cortical sheet) or, later, abstract spaces (for instance, that of neuron celltypes), in which the dynamics are highly regular in space and time. Recent improvements in recordings of neural activity have further demonstrated the smoothness of the neural dynamics, when placed in an appropriate embedding space.

@@

We show that embedding spaces are not unique, and more suprisingly, that we can find multiple embedding spaces in different dimensions, which all model identical neural dynamics.
The core of this work lies in the study of bijective mappings $S$ between $[0,1]^2$ and $[0,1]$, which allows mapping a two-dimensional neural field to an equivalent one-dimensional neural field.
This procedure is easily generalized to map between embeddings in arbitrary number of dimensions.
We introduce a measure of locality, which quantifies how the regularity of the neural fields in conserved through the mappings $S$. This allows us to show that the resulting neural field is well-behaved, and can therefore be approximated using classical grid-based methods.
To illustrate these results through numerical models, we describe a coarse-graining procedure enforcing the locality of the numerically applied mappings.

% Please keep the Author Summary between 150 and 200 words
% Use first person. PLOS ONE authors please skip this step. 
% Author Summary not valid for PLOS ONE submissions.   
\section*{Author summary}
Lorem ipsum dolor sit amet, consectetur adipiscing elit. Curabitur eget porta erat. Morbi consectetur est vel gravida pretium. Suspendisse ut dui eu ante cursus gravida non sed sem. Nullam sapien tellus, commodo id velit id, eleifend volutpat quam. Phasellus mauris velit, dapibus finibus elementum vel, pulvinar non tellus. Nunc pellentesque pretium diam, quis maximus dolor faucibus id. Nunc convallis sodales ante, ut ullamcorper est egestas vitae. Nam sit amet enim ultrices, ultrices elit pulvinar, volutpat risus.

\linenumbers

@@

Early recordings of cats' somatosensory \cite{Mou57} and visual \cite{HubWie62} cortices suggested that the cortical sheet is organized in vertical columns of functionally similar neurons.

The columnar organization of the cortex motivated the design of spatially structured models of neural population dynamics, namely neural field models \cite{WilCow73,Nun74,Ama77}, where the spatial dimensions corresponded to the two dimensions of the cortical sheet.

As models of spatiotemporal neural population dynamics on the cortical sheet, neural field models can be used to explain experimentally observed patterns of cortical activity, such as travelling waves in visual \cite{SatNau12,MulRey14}, somatosensory \cite{PetHah03,FerBol06}, motor \cite{RubRob06,TakKim15}, and hippocampal \cite{LubSia09,PatFuj12,PatSch13} cortices (see \cite{MulCha18} for a review), and are used to model large-scale brain signals, such as electroencephalography (EEG) recordings \cite{Bre17} (see also \cite{DipRan18} for an example of neural field modelling of calcium imaging recording of the visual cortex).

More recent recording methods, especially in rodents, have provided evidence of low-dimensional organization of neuronal activity that does not depend on the physical locations of neurons on the cortical sheet. For example, contrary to cats' visual cortex, the orientation selectivity of pyramidal neurons in a rat's visual cortex does not depend on their locations, that is, orientation selectivity is heterogeneous at any given location \cite{OhkChu05}. Moreover, the activity of interneurons in any small volume of the visual cortex is also heterogeneous and seems to be structured by a low-dimensional manifold of fine cell subtypes \cite{BugDuf22}. The local functional heterogeneity of neuronal activity in the cortex challenges the old concept of functionally homogeneous cortical columns and, with it, classical neural field models.

While, historically, the spatial dimensions in neural field models have been the two dimensions of the cortical sheet (with the notable exception of the ring models for orientation selectivity in the visual cortex \cite{BenBar95} and the head-direction system \cite{Zha96}), the "space" in neural field models does not need to represent physical space but can represent any suitable abstract embedding space. Neural field models with abstract embedding spaces could constitute a generalization of classical neural field theory for cortical networks that are not solely structured by distances of neurons on the cortical sheet.

Moreover, this work is motivated by recent mathematical developments \cite{JabPoy21} in mean-field theories involving the theory of graphons. Informally, these results suggest that, as long as the connectivity scales as $1/N$ (where $N$ is the number of neurons), the dynamics of large networks can be described in the $N \to \infty$ limit by a neural field equation where the embedding is simply the interval $[0,1]$. The main contribution of this paper is the derivation of a method, allowing to explicitly write such a one-dimensional neural field, starting from a known higher-dimensional neural field.

@@

We begin our work by considering a neural field associated with a $p$-dimensional embedding $\Rp$. $h(\vec z, t)$ describes the potential of the neural population at position $\vec z=(z_1,\cdots,z_p)$ in the embedding. The connectivity kernel $w(\vec y, \vec z)$ describes the amplitude of the recurrent currents from the population at $\vec z$ to the population at $\vec y$. Importantly, $w(\vec y, \vec z)$ is a ``smooth'' function in both arguments. This is a natural consequence of the derivation of neural field equations (rigorous proofs of convergence of networks to neural fields are still an active area of study, and we may cite \cite{CheDua19,AGATHENERINE202286} for recent developments).
$\rho(\vec z)$ measures the number of neurons per unit volume of the embedding space, effectively weighing the recurrent currents. The monotonic increasing activation function $\phi(h)$ describes the firing rate of a given neuron (population) with potential $h$. The neural field then evolves according to \autoref{eq:nf-in-rp}:

@@

Let us define a sequence of bijective mappings $S^n$, acting on the $n$-bit truncations of $\vec{v_i}$, as well as the sequence $\alpha_i^n \in [0,1]$ of positions resulting from the image of $\vec{v_i^{(n)}}$. In the following, we again drop the index $i$ for clarity.

\begin{equation} \begin{aligned}
S^n &: (v_1^{(n)}, v_2^{(n)}) = (0.b_1^1 b_1^2 \cdots b_1^n, 0.b_2^1 b_2^2 \cdots b_2^n) \\
&\mapsto \alpha^n = 0.b^1 b^2 \cdots b^{2n}
\end{aligned} \end{equation}

We note that we write $\alpha^n$ using $2n$ bits, which is intuitively the lowest number of bits required so that $S^n$ remains a bijection. More than $2n$ bits could be allowed while maintaining bijectivity, but we omit this possibility, since they wouldn't strictly be required. Effectively, $S^n$ maps between $2\times n$ input bits and $2n$ output bits. In this formulation, it becomes clear that in order to be a bijection, every bit of the input must be used once and only once to form the output. Setting aside bit inversions, this means that $S^n$ defines a permutation of the $2n$ input bits. [TODO: are more details necessary ? I think this is clear enough, though in the thesis manuscript I got over this point in more detail]

@@

% Use "Eq" instead of "Equation" for equation citations.
% \section*{Introduction}
% Lorem ipsum dolor sit~\cite{bib1} amet, consectetur adipiscing elit. Curabitur eget porta erat. Morbi consectetur est vel gravida pretium. Suspendisse ut dui eu ante cursus gravida non sed sem. Nullam Eq~(\ref{eq:schemeP}) sapien tellus, commodo id velit id, eleifend volutpat quam. Phasellus mauris velit, dapibus finibus elementum vel, pulvinar non tellus. Nunc pellentesque pretium diam, quis maximus dolor faucibus id.~\cite{bib2} Nunc convallis sodales ante, ut ullamcorper est egestas vitae. Nam sit amet enim ultrices, ultrices elit pulvinar, volutpat risus.

% \begin{eqnarray}
% \label{eq:schemeP}
% 	\mathrm{P_Y} = \underbrace{H(Y_n) - H(Y_n|\mathbf{V}^{Y}_{n})}_{S_Y} + \underbrace{H(Y_n|\mathbf{V}^{Y}_{n})- H(Y_n|\mathbf{V}^{X,Y}_{n})}_{T_{X\rightarrow Y}},
% \end{eqnarray}

% \section*{Materials and methods}
% \subsection*{Etiam eget sapien nibh}

% % For figure citations, please use "Fig" instead of "Figure".
% Nulla mi mi, Fig~\ref{fig1} venenatis sed ipsum varius, volutpat euismod diam. Proin rutrum vel massa non gravida. Quisque tempor sem et dignissim rutrum. Lorem ipsum dolor sit amet, consectetur adipiscing elit. Morbi at justo vitae nulla elementum commodo eu id massa. In vitae diam ac augue semper tincidunt eu ut eros. Fusce fringilla erat porttitor lectus cursus, \nameref{S1_Video} vel sagittis arcu lobortis. Aliquam in enim semper, aliquam massa id, cursus neque. Praesent faucibus semper libero.

% % Place figure captions after the first paragraph in which they are cited.
% \begin{figure}[!h]
% \caption{{\bf Bold the figure title.}
% Figure caption text here, please use this space for the figure panel descriptions instead of using subfigure commands. A: Lorem ipsum dolor sit amet. B: Consectetur adipiscing elit.}
% \label{fig1}
% \end{figure}

% % Results and Discussion can be combined.
% \section*{Results}
% Nulla mi mi, venenatis sed ipsum varius, Table~\ref{table1} volutpat euismod diam. Proin rutrum vel massa non gravida. Quisque tempor sem et dignissim rutrum. Lorem ipsum dolor sit amet, consectetur adipiscing elit. Morbi at justo vitae nulla elementum commodo eu id massa. In vitae diam ac augue semper tincidunt eu ut eros. Fusce fringilla erat porttitor lectus cursus, vel sagittis arcu lobortis. Aliquam in enim semper, aliquam massa id, cursus neque. Praesent faucibus semper libero.

% % Place tables after the first paragraph in which they are cited.
% \begin{table}[!ht]
% \begin{adjustwidth}{-2.25in}{0in} % Comment out/remove adjustwidth environment if table fits in text column.
% \centering
% \caption{
% {\bf Table caption Nulla mi mi, venenatis sed ipsum varius, volutpat euismod diam.}}
% \begin{tabular}{|l+l|l|l|l|l|l|l|}
% \hline
% \multicolumn{4}{|l|}{\bf Heading1} & \multicolumn{4}{|l|}{\bf Heading2}\\ \thickhline
% $cell1 row1$ & cell2 row 1 & cell3 row 1 & cell4 row 1 & cell5 row 1 & cell6 row 1 & cell7 row 1 & cell8 row 1\\ \hline
% $cell1 row2$ & cell2 row 2 & cell3 row 2 & cell4 row 2 & cell5 row 2 & cell6 row 2 & cell7 row 2 & cell8 row 2\\ \hline
% $cell1 row3$ & cell2 row 3 & cell3 row 3 & cell4 row 3 & cell5 row 3 & cell6 row 3 & cell7 row 3 & cell8 row 3\\ \hline
% \end{tabular}
% \begin{flushleft} Table notes Phasellus venenatis, tortor nec vestibulum mattis, massa tortor interdum felis, nec pellentesque metus tortor nec nisl. Ut ornare mauris tellus, vel dapibus arcu suscipit sed.
% \end{flushleft}
% \label{table1}
% \end{adjustwidth}
% \end{table}

% %PLOS does not support heading levels beyond the 3rd (no 4th level headings).
% \subsection*{\lorem\ and \ipsum\ nunc blandit a tortor}
% \subsubsection*{3rd level heading} 
% Maecenas convallis mauris sit amet sem ultrices gravida. Etiam eget sapien nibh. Sed ac ipsum eget enim egestas ullamcorper nec euismod ligula. Curabitur fringilla pulvinar lectus consectetur pellentesque. Quisque augue sem, tincidunt sit amet feugiat eget, ullamcorper sed velit. Sed non aliquet felis. Lorem ipsum dolor sit amet, consectetur adipiscing elit. Mauris commodo justo ac dui pretium imperdiet. Sed suscipit iaculis mi at feugiat.

% \begin{enumerate}
% 	\item{react}
% 	\item{diffuse free particles}
% 	\item{increment time by dt and go to 1}
% \end{enumerate}

% \subsection*{Sed ac quam id nisi malesuada congue}

% Nulla mi mi, venenatis sed ipsum varius, volutpat euismod diam. Proin rutrum vel massa non gravida. Quisque tempor sem et dignissim rutrum. Lorem ipsum dolor sit amet, consectetur adipiscing elit. Morbi at justo vitae nulla elementum commodo eu id massa. In vitae diam ac augue semper tincidunt eu ut eros. Fusce fringilla erat porttitor lectus cursus, vel sagittis arcu lobortis. Aliquam in enim semper, aliquam massa id, cursus neque. Praesent faucibus semper libero.

% \begin{itemize}
% 	\item First bulleted item.
% 	\item Second bulleted item.
% 	\item Third bulleted item.
% \end{itemize}

% \section*{Discussion}
% Nulla mi mi, venenatis sed ipsum varius, Table~\ref{table1} volutpat euismod diam. Proin rutrum vel massa non gravida. Quisque tempor sem et dignissim rutrum. Lorem ipsum dolor sit amet, consectetur adipiscing elit. Morbi at justo vitae nulla elementum commodo eu id massa. In vitae diam ac augue semper tincidunt eu ut eros. Fusce fringilla erat porttitor lectus cursus, vel sagittis arcu lobortis. Aliquam in enim semper, aliquam massa id, cursus neque. Praesent faucibus semper libero~\cite{bib3}.

% \section*{Conclusion}

% CO\textsubscript{2} Maecenas convallis mauris sit amet sem ultrices gravida. Etiam eget sapien nibh. Sed ac ipsum eget enim egestas ullamcorper nec euismod ligula. Curabitur fringilla pulvinar lectus consectetur pellentesque. Quisque augue sem, tincidunt sit amet feugiat eget, ullamcorper sed velit.

% Sed non aliquet felis. Lorem ipsum dolor sit amet, consectetur adipiscing elit. Mauris commodo justo ac dui pretium imperdiet. Sed suscipit iaculis mi at feugiat. Ut neque ipsum, luctus id lacus ut, laoreet scelerisque urna. Phasellus venenatis, tortor nec vestibulum mattis, massa tortor interdum felis, nec pellentesque metus tortor nec nisl. Ut ornare mauris tellus, vel dapibus arcu suscipit sed. Nam condimentum sem eget mollis euismod. Nullam dui urna, gravida venenatis dui et, tincidunt sodales ex. Nunc est dui, sodales sed mauris nec, auctor sagittis leo. Aliquam tincidunt, ex in facilisis elementum, libero lectus luctus est, non vulputate nisl augue at dolor. For more information, see \nameref{S1_Appendix}.

% \section*{Supporting information}

% % Include only the SI item label in the paragraph heading. Use the \nameref{label} command to cite SI items in the text.
% \paragraph*{S1 Fig.}
% \label{S1_Fig}
% {\bf Bold the title sentence.} Add descriptive text after the title of the item (optional).

% \paragraph*{S2 Fig.}
% \label{S2_Fig}
% {\bf Lorem ipsum.} Maecenas convallis mauris sit amet sem ultrices gravida. Etiam eget sapien nibh. Sed ac ipsum eget enim egestas ullamcorper nec euismod ligula. Curabitur fringilla pulvinar lectus consectetur pellentesque.

% \paragraph*{S1 File.}
% \label{S1_File}
% {\bf Lorem ipsum.}  Maecenas convallis mauris sit amet sem ultrices gravida. Etiam eget sapien nibh. Sed ac ipsum eget enim egestas ullamcorper nec euismod ligula. Curabitur fringilla pulvinar lectus consectetur pellentesque.

% \paragraph*{S1 Video.}
% \label{S1_Video}
% {\bf Lorem ipsum.}  Maecenas convallis mauris sit amet sem ultrices gravida. Etiam eget sapien nibh. Sed ac ipsum eget enim egestas ullamcorper nec euismod ligula. Curabitur fringilla pulvinar lectus consectetur pellentesque.

% \paragraph*{S1 Appendix.}
% \label{S1_Appendix}
% {\bf Lorem ipsum.} Maecenas convallis mauris sit amet sem ultrices gravida. Etiam eget sapien nibh. Sed ac ipsum eget enim egestas ullamcorper nec euismod ligula. Curabitur fringilla pulvinar lectus consectetur pellentesque.

% \paragraph*{S1 Table.}
% \label{S1_Table}
% {\bf Lorem ipsum.} Maecenas convallis mauris sit amet sem ultrices gravida. Etiam eget sapien nibh. Sed ac ipsum eget enim egestas ullamcorper nec euismod ligula. Curabitur fringilla pulvinar lectus consectetur pellentesque.

% \section*{Acknowledgments}
% Cras egestas velit mauris, eu mollis turpis pellentesque sit amet. Interdum et malesuada fames ac ante ipsum primis in faucibus. Nam id pretium nisi. Sed ac quam id nisi malesuada congue. Sed interdum aliquet augue, at pellentesque quam rhoncus vitae.

\nolinenumbers
